---
title: "ASSIGNMENT 7"
author: "Saurabh Shrestha"
date: '2021-05-03'
output:
  word_document: default
  html_document: default
  pdf_document: default
bibliography: C:/Users/Saurabh/Desktop/DSC 520/Week2/dsc520
---


## Set the working directory to the root of your DSC 520 directory
```{r}
setwd("C:/Users/Saurabh/Desktop/DSC 520")
```

## Load the `data/r4ds/heights.csv` to
```{r}
student_df <- read.csv("C:/Users/Saurabh/Desktop/DSC 520/Week2/dsc520/data/student-survey.csv")
head(student_df)
```

i. Use R to calculate the covariance of the Survey variables and provide an explanation
of why you would use this calculation and what the results indicate."
```{r}
cov(student_df)
```
"The reason is it shows how time reading with time spent on tv and happiness is
interrelated. Higher time reading means less time spent on tc but happiness
is negative whereas higher time spent on tv lead to higher level of happiness."

"ii. Examine the Survey data...."
"Time reading in hours
Time on TV is on minutes
Happiness is on a scale of 1-100
Gender is binary which is 0 and 1
A different measurement applicable or which would be used is genre of 
books and time of the day and another measurement would be changing the time:since
both time spent on tv and time spend reading book would have been converted into 
minutes. This would give us approx exact minute to minute variance of association
between the variables."

"iii. Choose the type of correlation test to perform."
"To get single corelation coefficient I used only the variables because by 
default this function produces Pearson's r and a 95% confidence interval
95% confidence ranged from -.969 to -.602 which does not 
cross zero which tells us that in time reading and time on tv is negatively 
related."
```{r}
cor.test(student_df$TimeReading, student_df$TimeTV)
```

#iv.Perform a correlation analysis of...
#1.
```{r}
cor(student_df)
111
#2.
```{r}
cor(student_df$TimeReading, student_df$TimeTV, use = "complete.obs", method = "pearson")
```
#3.
```{r}
cor.test(student_df$TimeReading, student_df$TimeTV, use = "complete.obs", method = "pearson", conf.level = 0.95)
```
#4.
The relationship between variables based on the student survey matrix suggests that
students who spend more on reading tend to spend less time watching tv 
and higher time spent on tv lead to increase in happiness."

#v.
# correaltion coefficient
```{r}
cor(student_df, use = "complete.obs", method = "pearson")
```
# coefficient of determination
```{r}
cor(student_df)^2
```

Above we squared the student survey variables by usin ^2. This way we can see
that how much of the variability in Time reading is shared by happiness
and how much variability in Time spend on tv is shared by happiness.


#vi.
cor(student_df$TimeReading, student_df$TimeTV)^2
"Based on correlation of determination, it shows 0.77 which converted
to percentage is 77% of variablity
between students time reading with time spent on tv."



#vii. Pick three variables and perform a partial correlation..."
```{r}
install.packages("ggm")
library(ggm)
partial_correlation <- pcor(c("TimeReading", "TimeTV", "Happiness"), var(student_df))
partial_correlation^2g, suicides)
```
